BOLD Parameter Estimation Using Particle Filters

### 2010-07-23 doc/thesis/resultsB.tex
more images, finalized parameter map output.
removes some duplicate labels

%23-10-18 or in original coordinates 36-17-19
\begin{figure}
\subfigure[Particle Filter]{\label{fig:comp5pfilter} \includegraphics[clip=true,trim=5cm 1cm 4cm 1cm,width=15cm]{images/6_pfilter_36_17_19}}\\
\subfigure[SPM]{\label{fig:comp5spm} \includegraphics[clip=true,trim=5cm 1cm 4cm 1cm,width=15cm]{images/6_spm_36_17_19}}
\caption{Section 6, MI of $0.335504$, T Value: $2.49154$, normalized error: $0.783348$ Not visible in SPM}
\label{fig:comp6}
\end{figure}

%16-19-0 or in original coordinates 29-26-1
\begin{figure}
\subfigure[Particle Filter]{\label{fig:comp5pfilter} \includegraphics[clip=true,trim=5cm 1cm 4cm 1cm,width=15cm]{images/7_pfilter_29_26_1}}\\
%\subfigure[SPM]{\label{fig:comp5spm} \includegraphics[clip=true,trim=5cm 1cm 4cm 1cm,width=15cm]{images/5_spm_25_34_25}}
\caption{Section 7, $.1052$ in MI, $1.31534$ in SPM (which left this flat) and $1.09992$ normalized $\sqrt{MSE}$. Only visible in MI map. }
\label{fig:comp7}
\end{figure}

Voxel 6 (\autoref{comp6}) is another region that is active according to both metrics used
in this work, yet was missed by SPM. The time series in \autoref{comp6} shows an extremely
good fit, perhaps the best in this batch, for the particle filter. In contrast, the
fit for SPM is abysmal. In spite of the fact that several other areas around are active
as well, the smoothing seems to have completely wiped out activation in this voxel.

@@

\section{Parameter Estimates}
Although the parameters are not uniquely identifiable by a single time-series, that
does not mean estimating them is not without benefit. The parameters still contain useful
information about the system. Additionally, as an aggregate they form a distribution of
the feasible parameters parameters for a particular patient. Therefore \autoref{fig:parammaps}
contains the parameter maps for the system and \autoref{} is a histogram across all voxels
for which the mutual information was greater than $.15$. As before, the threshold is not
scientifically derived, yet in tests this threshold provided a decent balance to remove most
of the questionably active voxels in the system.

\begin{figure}
\centering
\subfigure[$\tau_0$, Slice 6]{\includegraphics[width=7cm]{images/param_0000_6}}
\subfigure[$\tau_0$, Slice 7]{\includegraphics[width=7cm]{images/param_0000_7}}
\subfigure[$\alpha$, Slice 6]{\includegraphics[width=7cm]{images/param_0001_6}}
\subfigure[$\alpha$, Slice 7]{\includegraphics[width=7cm]{images/param_0001_7}}
\subfigure[$E_0$, Slice 6]{\includegraphics[width=7cm]{images/param_0002_6}}
\subfigure[$E_0$, Slice 7]{\includegraphics[width=7cm]{images/param_0002_7}}
\subfigure[$V_0$, Slice 6]{\includegraphics[width=7cm]{images/param_0003_6}}
\subfigure[$V_0$, Slice 7]{\includegraphics[width=7cm]{images/param_0003_7}}
\end{figure}

\begin{figure}
\centering
\subfigure[$\tau_f$, Slice 6]{\includegraphics[width=7cm]{images/param_0004_6}}
\subfigure[$\tau_f$, Slice 7]{\includegraphics[width=7cm]{images/param_0004_7}}
\subfigure[$\tau_s$, Slice 6]{\includegraphics[width=7cm]{images/param_0005_6}}
\subfigure[$\tau_s$, Slice 7]{\includegraphics[width=7cm]{images/param_0005_7}}
\subfigure[$\epsilon$, Slice 6]{\includegraphics[width=7cm]{images/param_0006_6}}
\subfigure[$\epsilon$, Slice 7]{\includegraphics[width=7cm]{images/param_0006_7}}
\caption{Parameter Map of two regions of interest ($M.I. > .15$).}
\label{fig:ParameterMap}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[clip=truew,trim=8cm 4cm 8cm 4cm,width=16cm]{images/realhist}
\caption{Histogram of parameters in active regions ($M.I. > .15$).}
\label{fig:FinalHist}
\end{figure}

The parameter maps show consistency parameter across active regions, however, 
the histogram of parameter estimates across all regions with $M.I. > .15$ is the
more interesting result (\autoref{fig:FinalHist}).

>>>>

%23-10-18 or in original coordinates 36-17-19
\begin{figure}
\subfigure[Particle Filter]{\label{fig:comp6pfilter} \includegraphics[clip=true,trim=5cm 1cm 4cm 1cm,width=15cm]{images/6_pfilter_36_17_19}}\\
\subfigure[SPM]{\label{fig:comp6spm} \includegraphics[clip=true,trim=5cm 1cm 4cm 1cm,width=15cm]{images/6_spm_36_17_19}}
\caption{Section 6, MI of $0.335504$, T Value: $2.49154$, normalized error: $0.783348$ Not visible in SPM}
\label{fig:comp6}
\end{figure}

%16-19-0 or in original coordinates 29-26-1
\begin{figure}
\subfigure[Particle Filter]{\label{fig:comp7pfilter} \includegraphics[clip=true,trim=5cm 1cm 4cm 1cm,width=15cm]{images/7_pfilter_29_26_1}}\\
%\subfigure[SPM]{\label{fig:comp7spm} \includegraphics[clip=true,trim=5cm 1cm 4cm 1cm,width=15cm]{images/5_spm_25_34_25}}
\caption{Section 7, $.1052$ in MI, $1.31534$ in SPM (which left this flat) and $1.09992$ normalized $\sqrt{MSE}$. Only visible in MI map. }
\label{fig:comp7}
\end{figure}

Voxel 6 (\autoref{fig:comp6}) is another region that is active according to both metrics used
in this work, yet was missed by SPM. The time series in \autoref{fig:comp6} shows an extremely
good fit, perhaps the best in this batch, for the particle filter. In contrast, the
fit for SPM is abysmal. In spite of the fact that several other areas around are active
as well, the smoothing seems to have completely wiped out activation in this voxel.

@@

\section{Parameter Estimates}
Although the parameters are not uniquely identifiable by a single time-series, that
does not mean estimating them is not without benefit. The parameters still contain useful
information about the system. Additionally, as an aggregate they form a distribution of
the feasible parameters parameters for a particular patient. Therefore 
\autoref{fig:pmap0} through \autoref{fig:pmap6}
contain the parameter maps for the system and \autoref{fig:realhist} is a histogram across all voxels
for which the mutual information was greater than $.15$. As before, the threshold is not
scientifically derived, yet in tests this threshold provided a decent balance to remove most
of the questionably active voxels in the system.

\begin{figure}[H]
\centering
\subfigure{\includegraphics[width=13cm]{images/pmap0}}
\subfigure{\includegraphics[scale=.5]{images/pscale_00}}
\caption{$\tau_0$ Estimates}
\label{fig:pmap0}
\end{figure}

\begin{figure}[H]
\centering
\subfigure{\includegraphics[width=13cm]{images/pmap1}}
\subfigure{\includegraphics[scale=.5]{images/pscale_01}}
\caption{$\alpha$ Estimates}
\label{fig:pmap1}
\end{figure}

\begin{figure}[H]
\centering
\subfigure{\includegraphics[width=13cm]{images/pmap2}}
\subfigure{\includegraphics[scale=.5]{images/pscale_02}}
\caption{$E_0$ Estimates}
\label{fig:pmap2}
\end{figure}

\begin{figure}[H]
\centering
\subfigure{\includegraphics[width=13cm]{images/pmap3}}
\subfigure{\includegraphics[scale=.5]{images/pscale_03}}
\caption{$V_0$ Estimates}
\label{fig:pmap3}
\end{figure}

\begin{figure}[H]
\centering
\subfigure{\includegraphics[width=13cm]{images/pmap4}}
\subfigure{\includegraphics[scale=.5]{images/pscale_04}}
\caption{$\tau_f$ Estimates}
\label{fig:pmap4}
\end{figure}

\begin{figure}[H]
\centering
\subfigure{\includegraphics[width=13cm]{images/pmap5}}
\subfigure{\includegraphics[scale=.5]{images/pscale_05}}
\caption{$\tau_s$ Estimates}
\label{fig:pmap5}
\end{figure}

\begin{figure}[H]
\centering
\subfigure{\includegraphics[width=13cm]{images/pmap6}}
\subfigure{\includegraphics[scale=.5]{images/pscale_06}}
\caption{$\epsilon$ Estimates}
\label{fig:pmap6}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[clip=truew,trim=8cm 4cm 8cm 4cm,width=16cm]{images/realhist}
\caption{Histogram of parameters in active regions ($M.I. > .15$).}
\label{fig:realhist}
\end{figure}

The parameter maps show consistency parameter across active regions, however, 
the histogram of parameter estimates across all regions with $M.I. > .15$ is the
more interesting result (\autoref{fig:realhist}).
